\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-09-14 abstract.tex
abstract

With the growing practice of mechanizing language metatheories,
it has become ever more important that proof assistants
make it easy to write reusable, extensible code and proofs.
We ...

>>>>

With the growing practice of mechanizing language metatheories,
it has become ever more pressing that interactive theorem provers 
make it easy to write reusable, extensible code and proofs.
%
This paper presents a language design useful for extensible metatheory
mechanization in a proof assistant.
The new design achieves reuse and extensibility via a form of family
polymorphism, a seemingly object-oriented idea, that allows code and
proofs to be polymorphic to their enclosing families.
Our development addresses significant technical challenges that arise
from the underlying language being simultaneously functional,
dependently typed, a logic, and an interactive tool.
%
Our results include
\begin{enumerate*}
\item a prototypical implementation of the language design as a Coq plugin,
\item a formalization of the language design as a constructive type theory with inductive types,
\item proofs of strong guarantees afforded by the type theory,
and 
\item case studies showing how the new expressiveness naturally addresses real
programming challenges in metatheory mechanization.
\end{enumerate*}
